An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/learner.tex

The goal of learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
In general, the learner module has two parts.
The first part ($\S$\ref{subsec-rules}) 
is to learn rules to check configuration errors like
missing entry, ordering errors, and fine-grained value correlation errors. 
These errors tend to cause total system failures.
%Once the configuration file has been validated against such rules, 
%the user may choose to invoke a more sensitive constraint checker. 
The second part of the learner ($\S$\ref{subsec-constraints}) 
aims to derive 
constraints on entries to check for suspicious (or anomalous) values 
that may violate standard practice (like the example~4 in
$\S$\ref{sec-motiv}).

@@

The first part of the learner is to learn rules 
that must hold over multiple parts of a configuration file.

\para{A strawman solution.}
We now first present a strawman solution (employed by
previous work~\cite{santolucitoCAV, zhang14encore}) that uses 
a set of correct configuration files as a learning set, 
from which it was possible to derive rules 
that must hold with absolute certainty. 
However, in practice, it is difficult to obtain a set of files 
that is both guaranteed to be without misconfiguration 
and large enough to learn many rules of configuration files.
This usually requires manual verification of the learning set, 
which is prone to error.

>>>>

The goal of the learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
It has two components.
The first component ($\S$\ref{subsec-rules}) 
learns rules for checking misconfiguration errors like
missing entry, ordering, and fine-grained value correlation errors. 
These errors tend to cause total system failures.
%Once the configuration file has been validated against such rules, 
%the user may choose to invoke a more sensitive constraint checker. 
The second component ($\S$\ref{subsec-constraints}) 
aims to derive 
constraints on entries to check for suspicious (or anomalous) values 
that may violate standard practice. These anomalies can cause partial 
degradation of the system, such as significant reduction in performance, or even 
total failure as in Example~4 of $\S$\ref{sec-motiv}.

@@

The first component learns rules that must hold over 
multiple parts of a configuration file.

\para{A strawman solution.}
We now first present a strawman solution (employed by
previous work~\cite{santolucitoCAV, zhang14encore}) that uses 
a set of correct configuration files as a learning set, 
from which it is possible to derive rules 
that must hold with absolute certainty. 
In practice, however, it is difficult to obtain a set of files 
that is both guaranteed to be without misconfiguration 
and large enough to learn many rules of configuration files.
This usually requires manual verification of the learning set, 
which is prone to error.
